Exploatarea Software și Mai Departe: Dezvăluirea Vectorilor de Atac și Contra-Măsurilor în Calculul Modern / Software Exploitation and Beyond: Unveiling Attack Vectors and Countermeasures in Modern Computing

### 2023-06-24 paper.tex
wowowowowowo

\documentclass{article}
\usepackage{tikz}
\usetikzlibrary{matrix,shapes,arrows,positioning,decorations.pathreplacing,arrows.meta}
\usepackage{comment}
\usepackage{marginnote}
\usepackage{pgf}
\usepackage{xstring}
\usepackage{listings}
\usepackage{xcolor}

@@

\section{Motivation}%

Ever since my first encounter with the intricacies of reverse engineering and
binary exploitation, I've been completely engrossed in the enigmatic and
thrilling world of low-level computing. Each compiled binary, to me, is an
intricate puzzle waiting to be deciphered. Every line of assembly, every opcode,
and every bit is a brushstroke in an abstract painting that only a trained eye
can understand and appreciate. This appreciation for the art of reverse
engineering started when I participated in my first major CTF (Capture The Flag)
event called X-MAS CTF, which was organized by the Hecarii Tuica si Paunii team.
Having spent countless hours trying to reverse algorithms in binaries, writing
two emulators for custom made platforms in the span of a week and bending
innocuous binaries to do my bidding and execute arbitrary commands revealed to
me how awesome an expansive this field of software security is. This paper will
only cover a small area of this large field and I urge the readers to explore
all of the fields of CyberSec.

@@

\section{Future trends}%

\section{Conclusion}%

\section{References}%

\end{document}

>>>>

\documentclass{article}
\usepackage{tikz}
\usetikzlibrary{matrix,shapes,arrows,positioning,decorations.pathreplacing,arrows.meta}
\usepackage{comment}
\usepackage{marginnote}
\usepackage{pgf}
\usepackage{xstring}
\usepackage{listings}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage[backend=biber,style=numeric]{biblatex}
\addbibresource{references.bib} % Import the bibliography file

@@

\section{Motivation}%
The ubiquity of digital devices in our daily lives has ushered in an era of
unprecedented data accessibility and convenience. Yet, these conveniences also
come with substantial security concerns. A significant proportion of the world's
population carries a device in their pocket that is not only a communication
device but also a gateway to their most personal and sensitive information,
including bank accounts, biometrics, and other data of significant value. These
devices, armed with cameras and microphones, could potentially be misused to
impersonate their owners. With these threats looming, the importance of rigorous
and effective exploit mitigation strategies, especially in system's programming,
cannot be overstated. These mitigation strategies form the critical defensive
layer that shields users from the consequences of potential security breaches,
preventing unauthorized access, and securing the private sphere of individuals
in the digital age. Hence, the motivation of this study is to evaluate, analyze,
and enhance the robustness of these mitigation strategies, thereby contributing
to safer and more secure software systems.

@@

\section{Future trends}%
Despite the recent shift in focus of threat actors towards exploiting the human
element -- the "weakest link" in the security chain -- through strategies such
as SIM swapping, targeted phishing attacks or weak passwords, it is crucial to
not diminish our emphasis on fortifying software against more technical
exploits. While these social engineering attacks have grown due to the
escalating complexity required to execute successful software exploits, they
should not detract from our progress in securing our software systems. The
mitigations that we have developed and deployed over the years have provided a
substantial defensive advantage in the realm of software exploitation. As the
future unfolds, maintaining this advantage will be of paramount importance, even
as we also strive to improve defenses against human-targeted
exploits.\cite{jones2021}\cite{smith2022}

\section{Conclusion}

\printbibheading
\printbibliography
\printbibliography[nottype=book,heading=subbibliography,title={Other Sources}]
\end{document}
